MCTS Based on Simple Regret

### 2012-01-27 paper/srcr/paper.tex
Bayesian MCTS

A completely different direction of controlling sampling can use the
principles of bounded rationality \cite{Horvitz.reasoningabout}
and meta-reasoning -  \cite{Russell.right} provided a formal
description of rational metareasoning and case studies of applications
in several problem domains. Using the principles of meta-reasoning,
one can ideally find an ``optimal'' sampling scheme, to be used
for selecting what to sample, both at the root node \cite{HayRussell.MCTS} and elsewhere.
However, this task is daunting for the following reasons:
\begin{itemize}
\item Defining the cost of a sample is not easy, and even just
  using time-cost as an approximation, we get an intractable
  meta-reasoning problem.
\item To handle the complexity, one must use simplifying assumptions.
      Applying the standard meta-reasoning myopic assumption, according to 
    which samples would be selected as though at most one sample
   can be taken before an action is chosen, we run into serious problems. Even the basic
  selection problem \cite{TolpinShimony.blinkered} exhibits a
  non-concave utility function and results in premature stopping of the
  standard myopic algorithms. This is due to the fact that the value of information of
  a single measurement (analogous to a sample in MCTS) is frequently
  less than its time-cost, even though this is not true for multiple
  measurements.  When applying the selection problem to MCTS, the
  situation is exacerbated.  The utility of an action is usually
  bounded, and thus in many cases a single sample may be insufficient
  to change the current best action, \emph{regardless} of its
  outcome. As a result, we frequently get a \emph{zero} ``myopic''
  value of information for a single sample.
\item Rational meta-reasoning requires a known distribution model, which may be
  difficult to obtain.
\end{itemize}

>>>>

A completely different direction of controlling sampling can use the
principles of bounded rationality \cite{Horvitz.reasoningabout}
and meta-reasoning ---  \cite{Russell.right} provided a formal
description of rational metareasoning and case studies of applications
in several problem domains. Using the principles of meta-reasoning,
one can ideally find an ``optimal'' sampling scheme, to be used
for selecting what to sample, both at the root node \cite{HayRussell.MCTS} and elsewhere.
However, this task is daunting for the following reasons:
\begin{itemize}
\item Defining the cost of a sample is not easy, and even just
  using time-cost as an approximation, we get an intractable
  meta-reasoning problem.
\item To handle the complexity, one must use simplifying assumptions.
      Applying the standard meta-reasoning myopic assumption, according to 
    which samples would be selected as though at most one sample
   can be taken before an action is chosen, we run into serious problems. Even the basic
  selection problem \cite{TolpinShimony.blinkered} exhibits a
  non-concave utility function and results in premature stopping of the
  standard myopic algorithms. This is due to the fact that the value of information of
  a single measurement (analogous to a sample in MCTS) is frequently
  less than its time-cost, even though this is not true for multiple
  measurements.  When applying the selection problem to MCTS, the
  situation is exacerbated.  The utility of an action is usually
  bounded, and thus in many cases a single sample may be insufficient
  to change the current best action, \emph{regardless} of its
  outcome. As a result, we frequently get a \emph{zero} ``myopic''
  value of information for a single sample.
\item Rational meta-reasoning requires a known distribution model, which may be
  difficult to obtain.
\end{itemize}
